\documentclass[a4paper,10pt]{moderncv}
%\moderncvstyle{banking}
%\moderncvcolor{blue}
\moderncvtheme[blue]{casual}
\usepackage[left=60pt,top=60pt,right=60pt,bottom=60pt]{geometry}
\usepackage[inline]{enumitem}

\usepackage[T1]{fontenc}
\usepackage{gfsdidot}

\setlength{\hintscolumnwidth}{0pt}
\linespread{1.04}


\firstname{Kesu} \familyname{Jayaprakash}
\address{Brampton, Ontario}{Canada  L6T 4N6} 
\phone{289-981-2649}
\email{kesu.jp.public@gmail.com}

\begin{document}
\maketitle

\section{POSITIONS}
\cvitem{}{\textbf{Sr. Java Developer (Consultant) at Rogers Communications Inc.}, Brampton ON Canada}
\cvitem{}{10/2013 -- current}
\cvitem{}{\begin{itemize}
    \item Working as a consultant for Rogers Communications Inc. in their provisioning systems department.
    \item Providing technical expertise for the development, testing and integration of wireless provisioning systems.
\end{itemize}}
\cvitem{}{\textbf{Development Group Leader at Amdocs Limited}, Limassol, Cyprus}
\cvitem{}{7/2005 -- 12/2012}
\cvitem{}{\begin{itemize}
    \item Lead development teams who implemented Amdocs OSS (Operations Support Systems) products for Tier-1 telecom operators.
    \item Designed and developed provisioning applications that met the low latency/high availability requirements of Telecom carriers.
    \item 5+ years experience in developing interfaces with mobile network infrastructure elements like HLR, Voice-mail systems, FNR, HSS etc.
    \item Received several certificates for innovations and demonstrating OSS product knowledge.
    \item Introduced automated unit testing in the division by integrating JUnit into in-house testing tools - reduced unit testing effort.
    \item Participated in requirement analysis sessions with clients, and derived the system requirements.
    \item Worked with business analysts and managers to provide development estimates.
    \item Wrote high level design documents/impact assessments and reviewed them with customers/vendors.
    \item Wrote external interface design documents based on vendor specifications, validated them with vendors.
    \item Reviewed detailed design documents, conducted code reviews and test case reviews.
    \item Utilized BPEL/BPMN and TIBCO tools for defining and capturing the system requirements.
\end{itemize}}
\cvitem{}{\textbf{Associate at Cognizant Technology Solutions, India}}
\cvitem{}{7/2003 -- 7/2005}
\cvitem{}{\begin{itemize}
    \item Recognized as ``Associate of the Month'' in the Dun \& Bradstreet (D\&B) account for innovations brought into routine development and support processes.
    \item Worked on projects that productized D\&B's business information database.
    \item Provided support for D\&B online systems that are used by D\&B business users.
    \item Implemented automated regression testing and integrated it into build - reduced the regression defects.
\end{itemize}}

\section{EDUCATION}
\cvitem{}{\textbf{Bachelor of Technology in Computer Science}, College of Engineering, Trivandrum, Kerala University}
\cvitem{}{6/1999 -- 7/2003}

\section{CERTIFICATIONS}
\cvitem{}{\textbf{R Programming.} Certificate earned on March 1, 2015 by Johns Hopkins University on Coursera}
\cvitem{}{\textbf{The Data Scientist's Toolbox.} Certificate earned on November 2, 2014 by Johns Hopkins University on Coursera}

\section{PROJECTS}
\cvitem{}{\textbf{Platform upgrade of Amdocs Activation Manager V7 to v8.2}, XL Axiata, Jakarta}
\cvitem{}{3/2012 -- 8/2012}
\cvitem{}{Excelcomindo (XL) is a leading telecommunication provider in Indonesia with subscriber base of more than 50 million. Lead the development team that upgraded their provisioning system to Amdocs AAM v8.2. The system integrated with network elements like HLR, EMA, FNR, BlackBerry server etc. using CLI (TCP/IP), SOAP, LDAP, REST etc. Extensive load testing was performed due to high transaction volume (4 million/day). The system went live with excellent quality figures.\newline
\textit{Technologies used: Java, J2EE, Weblogic, Web services, REST, Spring, Hibernate.}}
\cvitem{}{\textbf{New implementation of Amdocs Activation Manager 7.5}, Clearwire, USA}
\cvitem{}{1/2011 -- 9/2011}
\cvitem{}{Developed a WiMAX provisioning system. It was the first WiMAX provisioning project using Amdocs Activation Manager. Conducted on-site meetings with business analysts to gather requirements. Derived the system requirements for Amdocs Activation Manager and identified the non-functional requirements. Wrote high level design and interface design documents. The system integrated with various network elements like Bridgewater AAA, OMA/DM, Number portability system, E911, Oracle ESB and BlackBerry server.\newline
\textit{Technologies used: Java, Web services, Spring, Hibernate, Javascript}}
\cvitem{}{\textbf{New LTE provisioning system using Amdocs Activation Manager 7. 5}, MetroPCS Communications, USA}
\cvitem{}{3/2010 -- 6/2010}
\cvitem{}{MetroPCS Communications, Inc. is an American service provider with over 9.5 million subscribers. Lead the implementation of the Amdocs Activation Manager based solution for LTE provisioning. It was the first LTE provisioning project for Amdocs Activation Manager. The system integrated the HSS, PCRF and AAA systems with the Amdocs billing.\newline
\textit{Technologies used: Java, C++, Web services, Axis, XSLT}}

\section{SKILLS}
\cvitem{}{\textbf{Languages:} C/C++, Java, Python, Clojure, JavaScript, XML, SQL, XSLT}
\cvitem{}{\textbf{Tools \& Technologies:} JEE, EJB, JMS, Web Services, SOAP, REST, Hibernate, STL, JUnit, Pro*C, JQuery, MyBatis, scikit-learn}
\cvitem{}{\textbf{Other interests:} Agile Development, TDD, Functional Programming, C++11, Concurrent programming, Machine Learning, Big data}

\end{document}


